Automated Synthesis of State-Space Digital Systems

### 2016-12-12 cav2017/cav2017.tex
add comments to the paper

\textcolor{red}{LC: Cristina, may I ask you to expand further this section by connecting it to our control-synthesis work?}
\begin{figure}
\centering
\hspace*{-1cm}
\begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
},
          row sep=1cm, column sep=1.5cm] {
   \coordinate (aux1);
   \& \coordinate (aux2);
   \& ;\\
   \node[fill=yellow!20,align=center] (synth) {{\sc inductive}\\{\sc generalisation}};
   \&
   complexnode/.pic={ 
     \node[rectangle,draw,dashed,
	minimum width=6.7cm,
	minimum height=.8cm,
	label={\sc Validation oracles},] (verif) {};
   \node[fill=yellow!20] (verif1) at ([xshift=-2.1cm]verif.center) {{\sc Validate}};
   \node[fill=yellow!20,align=center] (verif2) at ([xshift=1.7cm]verif.center) {{\sc validate general}};
   } 
   \& \node[ellipse, fill=yellow!20] (done) {{\sc Done}};\\
   %% \node[fill=yellow!20] (verif) {{\sc ~~~~~~Uncertainty~~~~~~}};
   %% \&
   %% \node[fill=yellow!20] (verif2) {{\sc ~~~~~~Precision~~~~~~~}};\\
   \& \\
   \& \\
   \node (gp) {Program Search};
   \&
   complexnode/.pic={ 
     \coordinate (aux);
   \node (bmc) at ([xshift=-2.1cm]aux.center) {SAT/SMT Solver};
   \node (fp)  at ([xshift=1.9cm]aux.center) {SAT/SMT Solver};
   }   
    \\
  };

@@

@@

Finally, the matrices of the buck-boost converter are:
$$
\textbf{A}=\left[\begin{array}{cc}
0		& 375 \\
-3409	& -1515\\
\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
125 \\ 0 \\
\end{array}\right]~
\textbf{C}=\left[\begin{array}{cc}
0 & 1\\
\end{array}\right],~ \textbf{D}= 0.
$$.

>>>>

\textcolor{red}{LC: Dario and Cristina, may I ask you to expand further this section by connecting it to our control-synthesis work?}
\begin{figure}
\centering
\hspace*{-1cm}
\begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
},
          row sep=1cm, column sep=1.5cm] {
   \coordinate (aux1);
   \& \coordinate (aux2);
   \& ;\\
   \node[fill=yellow!20,align=center] (synth) {{\sc inductive}\\{\sc generalisation}};
   \&
   complexnode/.pic={ 
     \node[rectangle,draw,dashed,
	minimum width=6.7cm,
	minimum height=.8cm,
	label={\sc Validation oracles},] (verif) {};
   \node[fill=yellow!20] (verif1) at ([xshift=-2.1cm]verif.center) {{\sc Validate}};
   \node[fill=yellow!20,align=center] (verif2) at ([xshift=1.7cm]verif.center) {{\sc validate general}};
   } 
   \& \node[ellipse, fill=yellow!20] (done) {{\sc Done}};\\
   %% \node[fill=yellow!20] (verif) {{\sc ~~~~~~Uncertainty~~~~~~}};
   %% \&
   %% \node[fill=yellow!20] (verif2) {{\sc ~~~~~~Precision~~~~~~~}};\\
   \& \\
   \& \\
   \node (gp) {Program Search};
   \&
   complexnode/.pic={ 
     \coordinate (aux);
   \node (bmc) at ([xshift=-2.1cm]aux.center) {SAT/SMT Solver};
   \node (fp)  at ([xshift=1.9cm]aux.center) {SAT/SMT Solver};
   }   
    \\
  };

@@

\textcolor{red}{We will have to move this text to the beginning of the paper.}

@@

Finally, the matrices of the buck-boost converter are:
$$
\textbf{A}=\left[\begin{array}{cc}
0		& 375 \\
-3409	& -1515\\
\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
125 \\ 0 \\
\end{array}\right]~
\textbf{C}=\left[\begin{array}{cc}
0 & 1\\
\end{array}\right],~ \textbf{D}= 0.
$$
